# [`summarize()`]{.blue} to make rows/records with statistics. $_1$
 
 
### 
[summarize]{.blue}(tableName, newName = aggregateFunction)  
[summarize]{.blue}(tableName, aSum = sum(a), anAvg = mean(b), theVar = var(b)){.center} 
 
# What it does 

+ Make a new dataset with summary statistics
+ Use it to take a vector and output a single number
+ Only keeps the new variables
+ Base aggregate functions
    + min max mean median quantile sd var IQR diff length sum
+ dplyr aggregate functions
    + first last nth n n_distinct
  
 
# Demo code 


```{r theSummarizeTable, eval = FALSE}
laryngectomy |> 
{{  summarize(theMinFU = min(length_fu),}}
{{            theMeanFU = mean(length_fu),}}
{{            theMaxFU = max(length_fu))}}
```
]

```{r include=FALSE, warning=FALSE, message=FALSE}
library(tidyverse)
laryngectomy <- lr4ds::laryngectomy
```
```{r theSummarizeTableOut, echo=FALSE}
laryngectomy |> 
  summarize(theMinFU = min(length_fu),
            theMeanFU = mean(length_fu),
            theMaxFU = max(length_fu))
```
]
]
  
 
# Usefull stuff 

  
 
# Common Problems 

  
 
# Related Functions 
NA  
