# [`summarize()`]{.blue} to make rows/records with statistics. $_1$
.small[.center[[`summarize`]{.blue}`(tableName, newName = aggregateFunction)`  
[`summarize`]{.blue}`(tableName, aSum = sum(a), anAvg = mean(b), theVar = var(b))`]
+ Make a new dataset with summary statistics
+ Use it to take a vector and output a single number
+ Only keeps the new variables
+ Base aggregate functions
    + min max mean median quantile sd var IQR diff length sum
+ dplyr aggregate functions
    + first last nth n n_distinct
.pull-left-60[
```{r theSummarizeTable, eval = FALSE}
laryngectomy %>%
{{  summarize(theMinFU = min(length_fu),}}
{{            theMeanFU = mean(length_fu),}}
{{            theMaxFU = max(length_fu))}}
```
]
.pull-right-36[
```{r eval=FALSE, theSummarizeTableOut, echo=FALSE}
laryngectomy %>%
  summarize(theMinFU = min(length_fu),
            theMeanFU = mean(length_fu),
            theMaxFU = max(length_fu))
```
]
]
 
 
### NA{.center} 
 
# What it does 
NA  
 
# Demo code 
NA  
 
# Usefull stuff 
NA  
 
# Common Problems 
NA  
 
# Related Functions 
NA  
