# [`summarize()`]{.blue} to make rows/records with statistics. $_1$
 
 
### 
.small[[summarize]{.blue}(tableName, newName = aggregateFunction)  
[summarize]{.blue}(tableName, aSum = sum(a), anAvg = mean(b), theVar = var(b)){.center} 
 
# What it does 

+ Make a new dataset with summary statistics
+ Use it to take a vector and output a single number
+ Only keeps the new variables
+ Base aggregate functions
    + min max mean median quantile sd var IQR diff length sum
+ dplyr aggregate functions
    + first last nth n n_distinct
  
 
# Demo code 

.pull-left-60[
```{r theSummarizeTable, eval = FALSE}
laryngectomy %>%
{{  summarize(theMinFU = min(length_fu),}}
{{            theMeanFU = mean(length_fu),}}
{{            theMaxFU = max(length_fu))}}
```
]
.pull-right-36[
```{r theSummarizeTableOut, eval=FALSE, echo=FALSE}
laryngectomy %>%
  summarize(theMinFU = min(length_fu),
            theMeanFU = mean(length_fu),
            theMaxFU = max(length_fu))
```
]
]
  
 
# Usefull stuff 

.related-functions[]
  
 
# Common Problems 

  
 
# Related Functions 
NA  
