# Function name: summarize()
# Notes:
# [`summarize()`] to make rows/records with statistics. $_1$
.small[[[`summarize`]`(tableName, newName = aggregateFunction)`  
[`summarize`]`(tableName, aSum = sum(a), anAvg = mean(b), theVar = var(b))`]
+ Make a new dataset with summary statistics
+ Use it to take a vector and output a single number
+ Only keeps the new variables
+ Base aggregate functions
    + min max mean median quantile sd var IQR diff length sum
+ dplyr aggregate functions
    + first last nth n n_distinct
.pull-left-60[
```{r theSummarizeTable, eval = FALSE}
laryngectomy %>%
{{  summarize(theMinFU = min(length_fu),}}
{{            theMeanFU = mean(length_fu),}}
{{            theMaxFU = max(length_fu))}}
```
]
.pull-right-36[
```{r theSummarizeTableOut, eval = FALSE, echo=FALSE}
laryngectomy %>%
  summarize(theMinFU = min(length_fu),
            theMeanFU = mean(length_fu),
            theMaxFU = max(length_fu))
```
]
]
---


# Summarize Function

The summarize function is used to provide a concise summary of a dataset or a part of a dataset. It is often used to get an overall statistical summary of a dataset without having to look through all the individual values.

The summarize function can be found in the 'tidyverse' package. This package is widely used for data wrangling and contains a range of useful functions for data manipulation.

The summarize function should be used when a user wants to get a summary of a dataset, such as the number of observations and the mean, median